Milestone 2: Model Validation

### 2019-11-21 perf_release_criteria/milestone_3/ms_2_validation.Rmd
Fixing incorrect analysis using unmatched training Beta set for comparison, rather than validation. Updated accordingly.

df_beta_train <- df_train_f %>% filter(is_release == FALSE)
df_rel_train <- df_train_f %>% filter(is_release == TRUE)
n_beta <- nrow(df_beta_train)
```

@@

```{r nn_mal_fs1, echo=FALSE}
nn.mal.fs1 <- train_matchit(dfs[['4']], fs1, add_interactions = FALSE, replace = FALSE, 
                        caliper = 0.25, calclosest = TRUE, ratio = 2, distance = "mahalanobis")
nn.mal.fs1.qq <- build_quantile_df(df_rel_val, nn.mal.fs1$matched, df_beta_train)
nn.mal.fs1.score <- score_model(bts, nn.mal.fs1$matched, df_rel_val)
nn.mal.fs1.score
```

@@

```{r nn_mal_fs1_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.mal.fs1$matched, df_beta_train, nn.mal.fs1.qq)
```

@@

```{r nn_mal_fs3, echo=FALSE}
nn.mal.fs3 <- train_matchit(dfs[['16']], fs3, add_interactions = FALSE, replace = TRUE, 
                        caliper = 3.00, calclosest = TRUE, ratio = 1, distance = "mahalanobis")
nn.mal.fs3.qq <- build_quantile_df(df_rel_val, nn.mal.fs3$matched, df_beta_train)
nn.mal.fs3.score <- score_model(bts, nn.mal.fs3$matched, df_rel_val)
nn.mal.fs3.score
```
Number of Beta samples: `r nrow(nn.mal.fs3$matched)`

```{r nn_mal_fs3_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.mal.fs3$matched, df_beta_train)
```

@@

```{r nn_mal_fs5, echo=FALSE}
nn.mal.fs5 <- train_matchit(dfs[['8']], fs5, add_interactions = FALSE, replace = TRUE, 
                        caliper = 0, calclosest = TRUE, ratio = 1, 
                        distance = "mahalanobis")
nn.mal.fs5.qq <- build_quantile_df(df_rel_val, nn.mal.fs5$matched, df_beta_train)
nn.mal.fs5.score <- score_model(bts, nn.mal.fs5$matched, df_rel_val)
nn.mal.fs5.score
```

@@

```{r nn_mal_fs5_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.mal.fs5$matched, df_beta_train)
```

@@

```{r nn_logit_fs1, warning=FALSE, error=FALSE, echo=FALSE}
nn.linear.logit.fs1 <- train_matchit(dfs[['4']], fs1, add_interactions = TRUE, replace = FALSE, 
                        caliper = 0.4, calclosest = TRUE, ratio = 3, distance = "linear.logit")
nn.linear.logit.fs1.qq <- build_quantile_df(df_rel_val, nn.linear.logit.fs1$matched, df_beta_train)
nn.linear.logit.fs1.score <- score_model(bts, nn.linear.logit.fs1$matched, df_rel_val)
nn.linear.logit.fs1.score
```

@@

```{r nn_logit_fs1_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.linear.logit.fs1$matched, df_beta_train)
```

@@

```{r nn_logit_fs3, warning=FALSE, error=FALSE, echo=FALSE}
nn.linear.logit.fs5 <- train_matchit(dfs[['8']], fs5, add_interactions = FALSE, replace = FALSE, 
                        caliper = 0, calclosest = FALSE, ratio = 1, distance = "linear.logit")
nn.linear.logit.fs5.qq <- build_quantile_df(df_rel_val, nn.linear.logit.fs5$matched, df_beta_train)
nn.linear.logit.fs5.score <- score_model(bts, nn.linear.logit.fs5$matched, df_rel_val)
nn.linear.logit.fs5.score
```

```{r nn_logit_fs5_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.linear.logit.fs5$matched, df_beta_train)
```

@@

```{r nn_gam_fs1, warning=FALSE, error=FALSE, echo=FALSE, message=FALSE}
nn.gam.fs1 <- train_matchit(dfs[['4']], fs1, add_interactions = TRUE, replace = FALSE, 
                        caliper = 0.5, calclosest = TRUE, ratio = 3, distance = "GAMlogit")
nn.gam.fs1.qq <- build_quantile_df(df_rel_val, nn.gam.fs1$matched, df_beta_train)
nn.gam.fs1.score <- score_model(bts, nn.gam.fs1$matched, df_rel_val)
nn.gam.fs1.score
```

@@

```{r nn_gam_fs1_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.gam.fs1$matched, df_beta_train)
```

@@

```{r nn_gam_fs5, warning=FALSE, error=FALSE, echo=FALSE}
nn.gam.fs5 <- train_matchit(dfs[['4']], fs5, add_interactions = FALSE, replace = FALSE, 
                        caliper = 0, calclosest = FALSE, ratio = 1, distance = "GAMlogit")
nn.gam.fs5.qq <- build_quantile_df(df_rel_val, nn.gam.fs5$matched, df_beta_train)
nn.gam.fs5.score <- score_model(bts, nn.gam.fs5$matched, df_rel_val)
nn.gam.fs5.score
```

@@

```{r nn_gam_fs5_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.gam.fs5$matched, df_beta_train)
```

@@

```{r nn_probit_fs1, warning=FALSE, error=FALSE, echo=FALSE}
nn.linear.probit.fs1 <- train_matchit(dfs[['4']], fs1, add_interactions = TRUE, replace = FALSE, 
                        caliper = 0.4, calclosest = TRUE, ratio = 3, distance = "linear.probit")
nn.linear.probit.fs1.qq <- build_quantile_df(df_rel_val, nn.linear.probit.fs1$matched, df_beta_train)
nn.linear.probit.fs1.score <- score_model(bts, nn.linear.probit.fs1$matched, df_rel_val)
nn.linear.probit.fs1.score
```

@@

```{r nn_probit_fs1_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.linear.probit.fs1$matched, df_beta_train)
```

@@

```{r nn_probit_fs5, warning=FALSE, error=FALSE, echo=FALSE}
nn.linear.probit.fs5 <- train_matchit(dfs[['8']], fs5, add_interactions = FALSE, replace = FALSE, 
                        caliper = 0, calclosest = FALSE, ratio = 1, distance = "linear.probit")
nn.linear.probit.fs5.qq <- build_quantile_df(df_rel_val, nn.linear.probit.fs5$matched, df_beta_train)
nn.linear.probit.fs5.score <- score_model(bts, nn.linear.probit.fs5$matched, df_rel_val)
nn.linear.probit.fs5.score
```

@@

```{r nn_probit_fs5_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.linear.probit.fs5$matched, df_beta_train)
```

@@

```{r genmatch_fs1, echo=FALSE}
genmatch.fs1.matched <- df_train_gen[fs1_results$matches$index.control,]
genmatch.fs1.qq <- build_quantile_df(df_rel_val, genmatch.fs1.matched, df_beta_train)
genmatch.fs1.score <- score_model(bts, genmatch.fs1.matched, df_rel_val)
genmatch.fs1.score
```

@@

```{r genmatch_fs1_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, genmatch.fs1.matched, df_beta_train)
```

@@

```{r genmatch_fs1_500, echo=FALSE}
genmatch.fs1.500.matched <- df_train_gen[fs1_500_results$matches$index.control,]
genmatch.fs1.500.qq <- build_quantile_df(df_rel_val, genmatch.fs1.500.matched, df_beta_train)
genmatch.fs1.500.score <- score_model(bts, genmatch.fs1.500.matched, df_rel_val)
genmatch.fs1.500.score
```

@@

```{r genmatch_fs1_500_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, genmatch.fs1.500.matched, df_beta_train)
```

@@

```{r genmatch_fs3, echo=FALSE}
genmatch.fs3.matched <- df_train_gen[fs3_results$matches$index.control,]
genmatch.fs3.qq <- build_quantile_df(df_rel_val, genmatch.fs3.matched, df_beta_train)
genmatch.fs3.score <- score_model(bts, genmatch.fs3.matched, df_rel_val)
genmatch.fs3.score
```

@@

```{r genmatch_fs3_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, genmatch.fs3.matched, df_beta_train)
```

@@

```{r genmatch_fs5, echo=FALSE}
genmatch.fs5.matched <- df_train_gen[fs5_results$matches$index.control,]
genmatch.fs5.qq <- build_quantile_df(df_rel_val, genmatch.fs5.matched, df_beta_train)
genmatch.fs5.score <- score_model(bts, genmatch.fs5.matched, df_rel_val)
genmatch.fs5.score
```

@@

```{r genmatch_fs5_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, genmatch.fs5.matched, df_beta_train)
```

>>>>

df_beta_train <- df_train_f %>% filter(is_release == FALSE)
df_beta_val <- df_validate_f %>% filter(is_release == FALSE)
df_rel_train <- df_train_f %>% filter(is_release == TRUE)
n_beta <- nrow(df_beta_val)
```

@@

```{r nn_mal_fs1, echo=FALSE}
nn.mal.fs1 <- train_matchit(dfs[['4']], fs1, add_interactions = FALSE, replace = FALSE, 
                        caliper = 0.25, calclosest = TRUE, ratio = 2, distance = "mahalanobis")
nn.mal.fs1.qq <- build_quantile_df(df_rel_val, nn.mal.fs1$matched, df_beta_val)
nn.mal.fs1.score <- score_model(bts, nn.mal.fs1$matched, df_rel_val)
nn.mal.fs1.score
```

@@

```{r nn_mal_fs1_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.mal.fs1$matched, df_beta_val, nn.mal.fs1.qq)
```

@@

```{r nn_mal_fs3, echo=FALSE}
nn.mal.fs3 <- train_matchit(dfs[['16']], fs3, add_interactions = FALSE, replace = TRUE, 
                        caliper = 3.00, calclosest = TRUE, ratio = 1, distance = "mahalanobis")
nn.mal.fs3.qq <- build_quantile_df(df_rel_val, nn.mal.fs3$matched, df_beta_val)
nn.mal.fs3.score <- score_model(bts, nn.mal.fs3$matched, df_rel_val)
nn.mal.fs3.score
```
Number of Beta samples: `r nrow(nn.mal.fs3$matched)`

```{r nn_mal_fs3_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.mal.fs3$matched, df_beta_val)
```

@@

```{r nn_mal_fs5, echo=FALSE}
nn.mal.fs5 <- train_matchit(dfs[['8']], fs5, add_interactions = FALSE, replace = TRUE, 
                        caliper = 0, calclosest = TRUE, ratio = 1, 
                        distance = "mahalanobis")
nn.mal.fs5.qq <- build_quantile_df(df_rel_val, nn.mal.fs5$matched, df_beta_val)
nn.mal.fs5.score <- score_model(bts, nn.mal.fs5$matched, df_rel_val)
nn.mal.fs5.score
```

@@

```{r nn_mal_fs5_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.mal.fs5$matched, df_beta_val)
```

@@

```{r nn_logit_fs1, warning=FALSE, error=FALSE, echo=FALSE}
nn.linear.logit.fs1 <- train_matchit(dfs[['4']], fs1, add_interactions = TRUE, replace = FALSE, 
                        caliper = 0.4, calclosest = TRUE, ratio = 3, distance = "linear.logit")
nn.linear.logit.fs1.qq <- build_quantile_df(df_rel_val, nn.linear.logit.fs1$matched, df_beta_val)
nn.linear.logit.fs1.score <- score_model(bts, nn.linear.logit.fs1$matched, df_rel_val)
nn.linear.logit.fs1.score
```

@@

```{r nn_logit_fs1_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.linear.logit.fs1$matched, df_beta_val)
```

@@

```{r nn_logit_fs3, warning=FALSE, error=FALSE, echo=FALSE}
nn.linear.logit.fs5 <- train_matchit(dfs[['8']], fs5, add_interactions = FALSE, replace = FALSE, 
                        caliper = 0, calclosest = FALSE, ratio = 1, distance = "linear.logit")
nn.linear.logit.fs5.qq <- build_quantile_df(df_rel_val, nn.linear.logit.fs5$matched, df_beta_val)
nn.linear.logit.fs5.score <- score_model(bts, nn.linear.logit.fs5$matched, df_rel_val)
nn.linear.logit.fs5.score
```

```{r nn_logit_fs5_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.linear.logit.fs5$matched, df_beta_val)
```

@@

```{r nn_gam_fs1, warning=FALSE, error=FALSE, echo=FALSE, message=FALSE}
nn.gam.fs1 <- train_matchit(dfs[['4']], fs1, add_interactions = TRUE, replace = FALSE, 
                        caliper = 0.5, calclosest = TRUE, ratio = 3, distance = "GAMlogit")
nn.gam.fs1.qq <- build_quantile_df(df_rel_val, nn.gam.fs1$matched, df_beta_val)
nn.gam.fs1.score <- score_model(bts, nn.gam.fs1$matched, df_rel_val)
nn.gam.fs1.score
```

@@

```{r nn_gam_fs1_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.gam.fs1$matched, df_beta_val)
```

@@

```{r nn_gam_fs5, warning=FALSE, error=FALSE, echo=FALSE}
nn.gam.fs5 <- train_matchit(dfs[['4']], fs5, add_interactions = FALSE, replace = FALSE, 
                        caliper = 0, calclosest = FALSE, ratio = 1, distance = "GAMlogit")
nn.gam.fs5.qq <- build_quantile_df(df_rel_val, nn.gam.fs5$matched, df_beta_val)
nn.gam.fs5.score <- score_model(bts, nn.gam.fs5$matched, df_rel_val)
nn.gam.fs5.score
```

@@

```{r nn_gam_fs5_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.gam.fs5$matched, df_beta_val)
```

@@

```{r nn_probit_fs1, warning=FALSE, error=FALSE, echo=FALSE}
nn.linear.probit.fs1 <- train_matchit(dfs[['4']], fs1, add_interactions = TRUE, replace = FALSE, 
                        caliper = 0.4, calclosest = TRUE, ratio = 3, distance = "linear.probit")
nn.linear.probit.fs1.qq <- build_quantile_df(df_rel_val, nn.linear.probit.fs1$matched, df_beta_val)
nn.linear.probit.fs1.score <- score_model(bts, nn.linear.probit.fs1$matched, df_rel_val)
nn.linear.probit.fs1.score
```

@@

```{r nn_probit_fs1_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.linear.probit.fs1$matched, df_beta_val)
```

@@

```{r nn_probit_fs5, warning=FALSE, error=FALSE, echo=FALSE}
nn.linear.probit.fs5 <- train_matchit(dfs[['8']], fs5, add_interactions = FALSE, replace = FALSE, 
                        caliper = 0, calclosest = FALSE, ratio = 1, distance = "linear.probit")
nn.linear.probit.fs5.qq <- build_quantile_df(df_rel_val, nn.linear.probit.fs5$matched, df_beta_val)
nn.linear.probit.fs5.score <- score_model(bts, nn.linear.probit.fs5$matched, df_rel_val)
nn.linear.probit.fs5.score
```

@@

```{r nn_probit_fs5_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.linear.probit.fs5$matched, df_beta_val)
```

@@

```{r genmatch_fs1, echo=FALSE}
genmatch.fs1.matched <- df_train_gen[fs1_results$matches$index.control,]
genmatch.fs1.qq <- build_quantile_df(df_rel_val, genmatch.fs1.matched, df_beta_val)
genmatch.fs1.score <- score_model(bts, genmatch.fs1.matched, df_rel_val)
genmatch.fs1.score
```

@@

```{r genmatch_fs1_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, genmatch.fs1.matched, df_beta_val)
```

@@

```{r genmatch_fs1_500, echo=FALSE}
genmatch.fs1.500.matched <- df_train_gen[fs1_500_results$matches$index.control,]
genmatch.fs1.500.qq <- build_quantile_df(df_rel_val, genmatch.fs1.500.matched, df_beta_val)
genmatch.fs1.500.score <- score_model(bts, genmatch.fs1.500.matched, df_rel_val)
genmatch.fs1.500.score
```

@@

```{r genmatch_fs1_500_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, genmatch.fs1.500.matched, df_beta_val)
```

@@

```{r genmatch_fs3, echo=FALSE}
genmatch.fs3.matched <- df_train_gen[fs3_results$matches$index.control,]
genmatch.fs3.qq <- build_quantile_df(df_rel_val, genmatch.fs3.matched, df_beta_val)
genmatch.fs3.score <- score_model(bts, genmatch.fs3.matched, df_rel_val)
genmatch.fs3.score
```

@@

```{r genmatch_fs3_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, genmatch.fs3.matched, df_beta_val)
```

@@

```{r genmatch_fs5, echo=FALSE}
genmatch.fs5.matched <- df_train_gen[fs5_results$matches$index.control,]
genmatch.fs5.qq <- build_quantile_df(df_rel_val, genmatch.fs5.matched, df_beta_val)
genmatch.fs5.score <- score_model(bts, genmatch.fs5.matched, df_rel_val)
genmatch.fs5.score
```

@@

```{r genmatch_fs5_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, genmatch.fs5.matched, df_beta_val)
```
